Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-10-13 paper/main.tex
discussion: stability of contrast v2

% but
Nevertheless, results suggest that localization performance depends on the
amount of available data and how well the feature space is modeled.
% what's going on
Despite performing a whole brain analysis, we do not find many (random) clusters
in single contrasts or even systematically across contrasts that hamper the
interpretation of results.\todo[inline]{god forgive me for this paragraph}.

% other clusters
\todo[inline]{where are no clusters? e.g. top-down / bottom-up
attention, eye movements (FEF) (cf. corbetta2002control) or memory (which
memory)?}

% BUT: amount of data
Nevertheless, localization performance is influenced on the amount of available
data\todo{give examples of contrast using less events in AV and AO} and well
events within categories matched on average the preferred stimulus type.
% example AV: data amount and category homogeneity
For example in the AV stimulus, we averaged different kind of movie cuts
regardless to the movie frames content.\todo[inline]{how well spatially
constrained are the clusters?}
% AO: stimulus categories
For example in the AO stimulus, nouns of the narrator that cue a switch to
another setting belong to different categories (s. above).
% AO: number of events
\todo[inline]{Number of events in which contrasts?}
% example for data amount AO: superior temporal cortex
In four of nine contrasts of the AO stimulus, we find significant
clusters in superior auditory cortices (including early auditory
cortices?)\todo{which exactly}
% conclusion
This suggests that variance correlating with lower level auditory processes was
(not) averaged (out) across trials\todo{which contrasts; A1 \& low-level
nuisance regressors?}
% foreshadowing of narrator by soundscape
Further, verbal cues are regularly forestalled by changes of the
soundscape.\todo{cross-modal control contrasts; all negative results at moment
of cuts but vse\_new > pe\_old): right RSC.}
% arnott
\todo[inline]{e.g. arnott2008crinkling find increased activations of PPA to
sound made by objects}
% hypothesis
We hypothesize that not just semantic information but also the mere changes of a
soundscape that cues a listener about a setting's spatial layout of could
correlate with increased activity in the PPA.
% conclusion: AO and AV stability
In summary, our results across add further evidence that model-driven analyses
can be run on data from naturalistic stimuli to isolate brain activity
correlating with specific perceptual processes.
% but
Nevertheless isolation performance relies on how well the model captures
different aspects of the stimuli's feature space.

>>>>

% but
Results also suggest that localization performance depends on the
amount of available data and how well the feature space is modeled.
% what's going on
Despite performing a whole brain analysis, we do not find many (random) clusters
in single contrasts or even systematically across contrasts that hamper the
interpretation of results.\todo[inline]{god forgive me for this paragraph}.
% null results regarding attention and eye movements
For example in the AV results, we do not find significant clusters that could be
attributed to cognitive processes like attention, eye movements, or
memory.\todo{which kind of memory}

% BUT: amount of data
Nevertheless, localization performance is influenced by the amount of available
data\todo{give examples of contrast using less events in AV and AO} and how well
events within categories matched on average the preferred stimulus type.
% example AV: data amount and category homogeneity
For example in the AV stimulus, we averaged different kind of movie cuts
regardless to the movie frames content.\todo[inline]{how well spatially
constrained are the clusters?}
% results
As a result, clusters are more widespread and reach into early visual cortex.

\todo[inline]{first: number of available events -> ``noise''}

\todo[inline]{second: category match -> ``localization performance''}

% AO: stimulus categories
For example in the AO stimulus, nouns of the narrator that cue a switch to
another setting belong to different categories (s. above).\todo[inline]{Number
of events in which contrasts?}
% example for data amount AO: superior temporal cortex
In four of nine contrasts of the AO stimulus, we find significant clusters in
superior auditory cortices (including early auditory cortices?)\todo{which
exactly}
% conclusion
This suggests that variance correlating with lower level auditory processes was
(not) averaged (out) across trials\todo{which contrasts; A1 \& low-level
nuisance regressors?}
% foreshadowing of narrator by soundscape
Further, verbal cues are regularly forestalled by changes of the
soundscape.\todo{cross-modal control contrasts; all negative results at moment
of cuts but vse\_new > pe\_old): right RSC.}
% arnott
\todo[inline]{e.g. arnott2008crinkling find increased activations of PPA to
sound made by objects}
% hypothesis
We hypothesize that not just semantic information but also the mere changes of a
soundscape that cues a listener about a setting's spatial layout of could
correlate with increased activity in the PPA.
% conclusion: AO and AV stability
In summary, our results across add further evidence that model-driven analyses
can be run on data from naturalistic stimuli to isolate brain activity
correlating with specific perceptual processes.
% but
Nevertheless isolation performance relies on how well the model captures
different aspects of the stimuli's feature space.
